Appendix

### 2018-06-08 manuscript/appendix.Rmd
add conny metric scatter plots to appendix

```{r stream_density-vs-link_length}
library(magrittr)

dplyr::select(nes_nws, 
              avg_link_length, 
              stream_density, 
              closest_lake_distance) %>%
dplyr::rename("Average Link Length" = avg_link_length,
              "Stream Density" = stream_density,
              "Closest Lake Distance" = closest_lake_distance) %>%
GGally::ggpairs(columns = c("Average Link Length", 
                            "Closest Lake Distance", 
                            "Stream Density"),
#                axisLabels = "none", 
                upper = list(continuous = "blank"),
                diag = list(continuous = "blank"),
                lower = list(continuous = "points")) +
  theme(strip.background = element_blank())

ggplot(data = nes_nws) + 
  geom_point(aes(x = avg_link_length, y = stream_density)) + 
  ylab("Stream density") + xlab("Average Link Length")
```

>>>>

```{r stream_density-vs-link_length}
test <- dplyr::select(nes_nws, 
              avg_link_length, 
              stream_density, 
              closest_lake_distance) %>%
dplyr::rename("Average Link Length" = avg_link_length,
              "Stream Density" = stream_density,
              "Closest Lake Distance" = closest_lake_distance) %>%
dplyr::mutate(`Closest Lake Distance` = `Closest Lake Distance` / 100, 
              `Average Link Length` = `Average Link Length` / 100)

pair_opts <- theme(axis.text = element_blank(), 
      axis.ticks = element_blank())

cowplot::plot_grid(
  ggplot(data = test) + 
    geom_point(aes(y = `Average Link Length`, x = `Stream Density`)) + 
    pair_opts,
  ggplot(data = test) + 
    geom_point(aes(y = `Average Link Length`, x = `Closest Lake Distance`)) + 
    ylab("") + pair_opts, 
  ggplot(data = test) + 
    geom_point(aes(y = `Closest Lake Distance`, x = `Stream Density`)) +
    pair_opts,
  ggplot() + geom_blank(),
  nrow = 2, ncol = 2)
```
